3D Magnetic modelling of ellipsoidal bodies

### 2017-01-19 manuscript/manuscript.tex
start the magnetic field produced by ellipsoid

The magnetic modelling of an ellipsoidal body is commonly performed
in a particular Cartesian coordinate system that is aligned 
with the body semi-axes
and has the origin coincident with the body centre.
For convenience, we denominate this particular coordinate 
system as \textit{local coordinate system}.
The relationship between the Cartesian coordinates 
$(\tilde{x}, \tilde{y}, \tilde{z})$ of a point in 
a local coordinate system and the Cartesian 
coordinates $(x, y, z)$ of the same point in the main
system is given by:
\begin{equation}
\tilde{\mathbf{r}} = \mathbf{V}^{\top} \left( \mathbf{r} - \mathbf{r}_{c} \right) \: ,
\label{eq:coord_transformation}
\end{equation}
where 
$\tilde{\mathbf{r}} = [\begin{array}{ccc} \tilde{x} & 
                                          \tilde{y} & 
                                          \tilde{z} \end{array} ]^{\top}$,
$\mathbf{r}$ and $\mathbf{r}_{c}$
are defined in equation \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
is defined according to equations \ref{eq:V_triaxial_prolate} or
\ref{eq:V_oblate}, depending on the ellipsoid type.

@@

\subsection{Magnetic scalar potential }

The methods commonly applied in the magnetic modelling of
ellipsoidal bodies make use of an auxiliary variable $\lambda$,
which is a real number.

>>>>

The magnetic modelling of an ellipsoidal body is commonly performed
in a particular Cartesian coordinate system that is aligned 
with the body semi-axes
and has the origin coincident with the body centre.
For convenience, we denominate this particular coordinate 
system as \textit{local coordinate system}.
The relationship between the Cartesian coordinates 
$(\tilde{x}, \tilde{y}, \tilde{z})$ of a point in 
a local coordinate system and the Cartesian 
coordinates $(x, y, z)$ of the same point in the main
system is given by:
\begin{equation}
\tilde{\mathbf{r}} = \mathbf{V}^{\top} \left( \mathbf{r} - \mathbf{r}_{c} \right) \: ,
\label{eq:coord_transformation}
\end{equation}
where 
$\tilde{\mathbf{r}} = [\begin{array}{ccc} \tilde{x} & 
                                          \tilde{y} & 
                                          \tilde{z} \end{array} ]^{\top}$,
$\mathbf{r}$ and $\mathbf{r}_{c}$
are defined in equation \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
is defined according to equations \ref{eq:V_triaxial_prolate} or
\ref{eq:V_oblate}, depending on the ellipsoid type.
Similarly, the transformation of a generic 
linear system $\mathbf{M} \mathbf{p} = \mathbf{d}$
referred to the main coordinate system into a new
linear system 
$\tilde{\mathbf{M}} \tilde{\mathbf{p}} = \tilde{\mathbf{d}}$
referred to a local coordinate system is given by
\begin{equation}
\tilde{\mathbf{M}} = \mathbf{V}^{\top} \mathbf{M} \mathbf{V} \: , 
\quad \tilde{\mathbf{p}} = \mathbf{V}^{\top} \mathbf{p} \: ,
\quad \tilde{\mathbf{d}} = \mathbf{V}^{\top} \mathbf{d} \: .
\label{eq:matrix_transformation}
\end{equation}

@@

\subsection{Magnetic field produced by ellipsoids}

Based on the mathematical theory of the magnetic 
induction developed by \citet{poisson1824}, 
\citet{maxwell1873} affirmed that, if $V$ is the 
gravitational potential produced by any body 
with uniform density $\rho$ and arbitrary shape at 
a point $(x, y, z)$, then $-\frac{\partial V}{\partial x}$
is the magnetic scalar potential produced 
at the same point by the same body 
if it has a uniform magnetization oriented along $x$ 
with intensity $\rho$.
\citet{maxwell1873} generalized this idea as a way
of determining the magnetic scalar potential produced
by any body uniformly magnetized in a given direction.
By presuming that this uniform magnetization is due to
induction, he postulated that the resulting magnetic
field intensity at all points within the body must
also be uniform and parallel the magnetization, which
results that the gravitational potential $V$ at points
within the body must be a quadratic function of the
spatial coordinates.
Apparently, \citet{maxwell1873} was the first one to
affirm that the only finite bodies having a gravitational
potential with this property and that, as a consequence,
can be uniformly magnetized in the presence of a uniform and 
static magnetic field are the ones bounded by surfaces 
of second degree, which are ellipsoids.

Let us start our description of the magnetic field produced
by ellipsoids by considering a magnetized ellipsoid immersed in
a uniform magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$).
The total magnetic intensity field $\mathbf{H}(\mathbf{r})$
at the position $\mathbf{r}$ (equations \ref{eq:A} and 
\ref{eq:coord_transformation}) of a point referred to the main 
coordinate system is defined as follows
\begin{equation}
\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla \phi(\mathbf{r}) \: ,
\label{eq:total-H-field}
\end{equation}
where the second term is the negative gradient of 
the magnetic scalar potential $\phi(\mathbf{r})$ given by
\begin{equation}
\phi(\mathbf{r}) = \frac{1}{4\pi} \iiint_{V} 
\mathbf{M}(\mathbf{r}^{\prime})^{\top} \left(
\frac{\mathbf{r} - \mathbf{r}^{\prime}}{\| \mathbf{r} - \mathbf{r}^{\prime} \|^{3}}
\right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
\label{eq:phi-potential}
\end{equation}
In this equation, $\mathbf{r}^{\prime} = [\begin{array}{ccc} 
x^{\prime} & y^{\prime} & z^{\prime} \end{array} ]^{\top}$
is the position vector of a point located within the volume $V$, 
the integral is conducted over the variables 
$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ representing
the coordinates of a point located within the volume $V$
of the ellipsoid, $\| \cdot \|$ denotes the Euclidean norm and 
$\mathbf{M}(\mathbf{r}^{\prime})$ is the magnetization vector
(in $\unit{Am^{-1}}$).
Equation \ref{eq:total-H-field} is valid anywhere, 
independently if the position vector $\mathbf{r}$ represents
a point located inside or outside the magnetized body.

Based on \citeauthor{maxwell1873}'s postulate, let us
assume that the body has a uniform magnetization given by
\begin{equation}
\mathbf{M} = \mathbf{K} \, \mathbf{H}_{i} \: ,
\label{eq:M-KH}
\end{equation}
where $\mathbf{H}_{i}$ is the resultant uniform magnetic field 
intensity at any point within the body and $\mathbf{K}$ is a 
constant and symmetrical 2nd-order tensor representing the 
magnetic susceptibility of the body. In this case, equation 
\ref{eq:total-H-field} can be rewritten as follows:
\begin{equation}
\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} 
- \mathbf{N}(\mathbf{r}) \, \mathbf{K} \, \mathbf{H}_{i} \: ,
\label{eq:total-H-field-M-uniform}
\end{equation}
where $\mathbf{N}(\mathbf{r})$ is a $3 \times 3$ matrix whose
$\alpha \beta$-element $n_{\alpha \beta}(\mathbf{r})$ is given by
\begin{equation}
n_{\alpha \beta}(\mathbf{r}) = - 
\frac{1}{4\pi} \frac{\partial^{2}}{\partial \alpha \, \partial \beta}
\iiint_{V} 
\frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
\, dx^{\prime}dy^{\prime}dz^{\prime} \: , \quad \alpha = x, y, z \: , 
\quad \beta = x, y, z \: .
\label{eq:n-alpha-beta}
\end{equation}

%
%This property comes from the fact that the gravitational potential
%within an ellipsoid with uniform density is a quadratic function
%of the spatial coordinates.
%
%Based on this, the magnetization vector
